A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-22 colt-21/cvx-flats.tex
changed def

Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}
\begin{definition}[Flat]\label{def:flat}\btw{Jessie: Suggest delete}
	A \emph{flat} $F \subseteq \affhull(\simplex)$ $\subseteq \reals^n$ is a nonempty set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ (relative to $\affhull(\simplex)$) is $n - \mathrm{rank}(W) - 1$.
\end{definition}

\jessie{Differentiate between $\ker$ and $\zeros$}
\begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

@@

\begin{definition}[$d$-representation]
	The flat $F \subseteq \P$ hass a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
\end{definition}

>>>>

Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.
Moreover, $\ker(W) = \{p \in \simplex : Wp = \vec 0\}$ is the kernel of matrix $W$.
%Recall that the affine hull is the set of all linear combinations whose coefficients sum to 1.
%In particular, we will often use \footnote{Recall $\affhull(\simplex) = \{\sum_{i=1}^n \alpha_i p_i : p_i \in \simplex, \alpha_i \in \reals, \sum_{i=1}^n \alpha_i = 1\}$, which has dimension $n-1$.}\jessiet{Space suggestion: move terse version of this to footnote.}

\begin{definition}[Flat]\label{def:flat-general}
	For $d\in\mathbb N$, a \emph{$d$-flat}, or simply \emph{flat} is a nonempty set $F = \zeros{W} = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.

@@

% \begin{definition}[$d$-representation]
% 	The flat $F \subseteq \P$ hass a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
% \end{definition}
